New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-04-20 main.tex
[wip] Reworking introduction

\newcommand{\eg}{{\textit{e.g.\xspace}}}
\newcommand{\etal}{{\textit{et al.\xspace}}}
\newcommand{\ie}{{\textit{i.e.\xspace}}}

@@

It is widely accepted that anthropomorphism describes a set of human-like
features of a robot (like shape, speech capabilities, facial expression).
Lemaignan~\etal~\cite{lemaignan2014dynamics}  refer to these characteristics as the
anthropomorphic design of the robot .  Anthropomorphism, as described by
Lemaignan~\etal, refers to the social phenomenon that emerges from the
interaction between a robot and an user. According to Epley~\etal
\cite{epley_when_2008},
this includes for instance emotional states, motivations, intentions ascribed by
the user to the robot.

Anthropomorphism is seen as a special kind of social (human-like) engagement
with robots. We made an attempt to analyze anthropomorphism in a
\textit{human-robot} interaction by utilizing the gaze patterns of the
participants (who watched this interaction). These gaze patterns were compared
to the gaze patterns for a similar \textit{human-human} interaction setting. The
``human'' part of the human-robot and human-human interactions mentioned above
is only in the form of an audio command and not physically present in the scene.
Hence, we represent the interactions with robot($\mathcal{R}$) and human($\mathcal{H}$) in
this report for the human-robot and human-human settings respectively.

@@

\section{Related Work}
\fxwarning{Need to modify (as S\'everin suggested) and curtail it}
In a human-robot interaction, studying anthropomorphism would essentially mean
the assessment of human's tendency to engage in a human like way with robots
(that are not deliberately made to buttress such relationship). In broader
terms, anthropomorphism can be understood as the phenomenon between a human and
a non-human, where the human tends to attribute human characteristics to the
non-human in order to establish a meaningful contact\cite{fink2014dynamics}. But
there have been a plethora of definitions of anthropomorphism not only across
but within disciplines\cite{duffy_anthropomorphism_2002}. Even
within HRI (human robot interaction) and robotics, there has not been a single
unique definition of anthropomorphism, but a variety of them.
Bartneck~\etal\cite{bartneck_measurement_2008} refer to it as \emph{``the
attribution of a human form, human characteristics, or human behavior to
nonhuman things such as robots, computers, and animals."} Contrarily,
Waytz~\etal\cite{Waytz2010} apply a more psychological-cognitive view and
define anthropomorphism as \textit{``a process of inductive inference whereby
    people imbue the real or imagined behavior of other agents with human like
    characteristics, motivations, intentions, or underlying mental states".}

Etymologically, anthropomorphism is a term composed of two Greek words :
\textit{anthropos} for ``man" (or ``human") and \textit{morphe} for ``from /
structure" (or ``shape"). Although anthropomorphism" literally would mean
``human form", it should \textit{not} be used to refer to the \textit{form/
design} of a non-human agent. The term \textbf{anthropomorphic design} would
rather be a better choice to refer to imitating human-like form / design of a
robot. Bartneck and Forlizzi\cite{bartneck_shaping_2004} recommend that \emph{form}
refers not just to the physical shape of a robot but to all ascertainable parts
of it. Therefore, ``form" could be seen as the overall expression of the robot,
that includes its shape, materials, and behavioral characteristics.
Anthropomorphic form can be broadly classified, but there is no fine line
dividing these categories: anthropomorphic, caricatured, functional,
zoomorphic (Fong \etal \cite{fong_survey_2003}).

Another key aspect in the discussion of anthropomorphism is the change in
people's perception of robots over their time of interaction with robots. And as
the perception changes, the tendency to anthropomorphize the robot is likely to
change. Such a gap related to the perceived agency of the robot was discussed by
Takayama \cite{takayama_perspectives_2012}. She noticed that among people who
own a robot, while some people perceive their robot as an agentic object, others
feel  it as only a plain machine. In order to distinguish between these two
patterns and make sense out of them in relation to people's perception of robots
in general, Takayama differentiated between what she calls an
\emph{in-the-moment} and a \emph{reflective} perspective on agency. Hence, an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation. On the other hand, a \emph{reflective}
perspective would indicate one's reaction/sense of a situation based on a more
in-depth  consideration and contemplation \cite{takayama_perspectives_2012}.

Quite often, these two distinctions are not considered differently, leading to
errors and confusions.  In other words, in an initial phase of interaction with
a non-human agent, people might respond ``mindlessly" instead of responding
consciously\cite{nass_machines_2000}. Only post a due amount of
time of, what is generally called as ``familiarization" with the robot, one
might respond in a more reflective manner instead of an in-the-moment reaction.
This can be demonstrated by the fact that when participants who had interacted
with a technology, were asked about whether the interaction with the technology
was in a human-like way, most of them denied this which shows the reflective
perspective . However, the same participants had actually reacted ( in the
moment of the interaction) to the system in many ways that were quite close to
how they would react to people\cite{reeves_media_1996}.

>>>>

\newcommand{\eg}{\textit{e.g.}\xspace}
\newcommand{\etal}{\textit{et al.}\xspace}
\newcommand{\ie}{\textit{i.e.}\xspace}
\newcommand{\etc}{\textit{etc.}\xspace}
\newcommand{\vs}{\textit{vs.}\xspace}

@@

Robotics researchers often tend to consider that anthropomorphism only describes
a static set of human-like features of a robot (like its shape, its speech
capabilities, facial expressions, etc.). We refer to these characteristics as
the \emph{anthropomorphic design} of the
robot~\cite{fink_anthropomorphism_2012}, and propose that
\emph{anthropomorphism} in general refers to a \emph{social phenomenon} that
emerges from the (real or imagined) interaction between a non-human agent (a
robot in our case) and a human~\cite{persson_anthropomorphism_2000}.  According
to~\cite{epley_when_2008}, anthropomorphism includes the human perception of
emotional states, motivations, intentions in the non-human agent, and tends to
ascribe those qualities to it. As such, the \textbf{dynamic and socio-cognitive
dimensions of anthropomorphism are essential to understand the complex bonds
that human users build with artificial agents such as
robots}~\cite{lemaignan2014dynamics}, and, even further, we postulate that
anthropomorphism can therefore be considered as a useful \emph{proxy} to these
intricate psychological bonds. This article aims at advancing our understanding
of this phenomenon \textbf{by evidencing the impact of the cognitive
presuppositions implied by the context of the interaction}.

The study of context in HRI is not new. \textit{Context of use} is defined by
the ISO as \textit{``users, tasks, equipment (hardware, software and materials),
and the physical and social environments in which a product is used''}, and
accordingly, there are various aspects that can impact how a robot is
experienced. The real or imagined \textit{purpose} of a robot, including the
application context in which it is typically used (\eg office environment, home,
rehabilitation center, public space, \etc) as well as the task context (\eg
serious or playful task; composition of human-robot team; number of users) and
the (social) role in which the robot is used / experienced are taken into
account. Generally, when the context of use of a robot is social, entertaining
or playful, it will enhance anthropomorphism, compared to when the context is a
routine or focused serious task (security, rescue, \etc).
\cite{joosse_what_2013} showed, for instance, that when the same robot ({\sc
nao}) was used in a different task context (cleaning task \vs tour guide), users
ascribed different personalities to the robot. \cite{goetz_cooperation_2002}
revealed a link between a robot's context of use and people's perception of the
robot: the authors found that people prefer a serious robot for serious tasks
and a less serious robot for more playful tasks. \cite{kaplan_free_2000}
discussed the role of uselessness in the design of robots. The author argues
that artificial pets like AIBO have no real purpose, in a sense that they do not
provide any kind of service or, in other words, \textit{``they are not doing
what you tell them to do''} and \textit{``they might refuse the order of its
owner''}. It may be this very aspect that increases people's tendency to
anthropomorphize the robot. According to Kaplan, it is in our daily use language
that we tend to attribute intentions to devices that are not doing their job
well.

These previous studies investigated users' perception of robots in
different prototyped tasks (routine vs playful, typically boring vs typically
intellectual) and their results nicely supported our general intuition.
In this article, we show that much more subtle variations in the task context do
lead to very noticeable effects as well.

Measuring anthropomorphism raises interesting methodological challenges, if only
tbecause people's perception of robots change over the duration of their
interaction with the robots. Takayama discusses the effects of this
change~\cite{takayama_perspectives_2012} and differentiates between what she calls an
\emph{in-the-moment} and a \emph{reflective} perspective on agency: an
\emph{in-the-moment} perspective would refer to one's most immediate
response/sense in a given situation, while a \emph{reflective}
perspective would indicate one's reaction/sense of a situation based on a more
in-depth  consideration and contemplation.

Quite often, these two distinctions are not considered differently, leading to
errors and confusions.  In other words, in an initial phase of interaction with
a non-human agent, people might respond ``mindlessly'' instead of responding
consciously~\cite{nass_machines_2000}. Only post a due amount of
time of, what is generally called as ``familiarization'' with the robot, one
might respond in a more reflective manner instead of an in-the-moment reaction.
This can be demonstrated by the fact that when participants who had interacted
with a technology, were asked about whether the interaction with the technology
was in a human-like way, most of them denied this which shows the reflective
perspective . However, the same participants had actually reacted ( in the
moment of the interaction) to the system in many ways that were quite close to
how they would react to people~\cite{reeves_media_1996}.

Most of the experiments that investigate anthropomorphism in HRI are conducted
in controlled lab-settings during a short-term scenario. For instance, pictures
or videos of different robots are shown to human subjects who subsequently fill
in a questionnaire, to assess how far the different types of robots were
perceived human-like. Such experimental settings have limitations for studying a
social phenomenon like anthropomorphism, and one may wonder if anthropomorphism
can really be measured in a post-interaction closed questionnaire or by rating
scales. Findings might possibly lead to interpretations that would not be
generalizable to natural settings or real interaction scenarios (which is always
an issue in social science research).

The Godspeed questionnaire~\citep{bartneck_measurement_2008}, and in particular,
its subpart focused on anthropomorphism, is the main validated questionnaire to
assess anthropomorphism. On 5 point semantic differential scales, people are
asked to rate the following constructs: fake \vs natural, machinelike \vs
humanlike, unconscious \vs conscious, artificial \vs lifelike, moving rigidly
\vs moving elegantly. Because the concept of ``human-likeness'' itself is
complex and abstract, \cite{kahn_jr._robotic_2006} suggest to ask for more
concrete constructs that are typical or unique of the concept of
``human-likeness'', and \cite{ruijten_introducing_2014} propose for instance a
25-item questionnaire to measure various concrete aspects of human-likeness.

\subsection{Hypotheses}

@@
